Presentation Title

### 2017-08-07 thesis/chapters/ch1-intro.tex
Fixes

Using the aforementioned insight,
we explore an alternative consensus model for blockchain systems where transactions themselves do not reach consensus,
but nevertheless verifiable at a later stage by any node in the network.
Informally, our system works as follows.
Every node stores its own blockchain and every block is one transaction.
We randomly select nodes in every round, the selected ones are called facilitators.
Facilitators reach consensus not on the individual transactions,
but on the state of every chain represented by a single digest, called a checkpoint block.
If a checkpoint block of some node is in consensus, 
then that node can proof to any other node that it holds a set of transactions that compute (form a chain) to the checkpoint block.
This immediately shows that those transactions are tamper-proof.
We call our protocol Checo, derived from \emph{che}ckpoint \emph{co}nsensus.
% TODO mention consensus and trade off?

>>>>

Using the aforementioned insight,
we explore an alternative consensus model for blockchain systems where transactions themselves do not reach consensus,
but nevertheless verifiable at a later stage by any node in the network.
We call our protocol Checo, derived from \emph{che}ckpoint \emph{co}nsensus.
Informally, our system works as follows.
Every node stores its own blockchain and every block is one transaction.
We randomly select nodes in every round, the selected ones are called facilitators.
Facilitators reach consensus not on the individual transactions,
but on the state of every chain represented by a single digest, called a checkpoint block.
If a checkpoint block of some node is in consensus, 
then that node can proof to any other node that it holds a set of transactions that compute (form a chain) to the checkpoint block.
This immediately shows that those transactions are tamper-proof.
The key difference from related work is the independence of the transaction validation phase.
Prior systems such a Bitcoin and Ethereum entangled the consensus algorithm with the transaction validation, restricting performance.
By splitting this functionality we achieved horizontal scalability in the general case.

### 2017-08-07 thesis/chapters/ch3-model.tex
Fixes

\subsection{Using epidemic protocol to reduce communication cost}
One of the final steps in our consensus protocol is to broadcast the consensus result and signatures to every other node (\Cref{sec:consensus-phase}).
While this guarantees delivery (since we assumed reliable channel), it is wasteful.
For example, if every facilitator is honest, a node would receive $n$ consensus results which are identical when only one is necessary.

An optimisation we can do is to use an epidemic protocol~\cite{eugster2004epidemic} (also known as gossiping) instead of our broadcast approach.
Typical epidemic protocols works as follows.
Every node buffers every message it receives up to some buffer size $b$.
Then it forwards the messages $t$ number of times.
Every time the message is sent to $f$ random neighbours, $f$ is often called the fan-out.
The upside of using epidemic protocol is that the communication cost is distributed more evenly between nodes.
This is especially true with a lazy push approach where the node who just received a message would push the message ID (e.g. digest) to its $f$ random neighbours,
and only push the full message if the neighbour explicitly requests the message~\cite{leitao2007epidemic}.
With this, nodes typically only need to receive one consensus result message instead of $n$.

>>>>

\subsection{Using epidemic protocol to reduce communication cost}
One of the final steps in our consensus protocol is to broadcast the consensus result and signatures to every other node (\Cref{sec:consensus-phase}).
While this guarantees delivery (since we assumed reliable channel), it is wasteful.
For example, if every facilitator is honest, a node would receive $n$ consensus results which are identical when only one is necessary.
Furthermore, realistic networks do not offer a broadcast primitive,
i.e. firewalls may block incoming messages from certain nodes.

An improvement is use an epidemic protocol~\cite{eugster2004epidemic} (also known as gossiping) instead of our broadcast approach.
Typical epidemic protocols works as follows.
Every node buffers every message it receives up to some buffer size $b$.
Then it forwards the messages $t$ number of times.
Every time the message is sent to $f$ random neighbours, $f$ is often called the fan-out.
The upside of using epidemic protocol is that the communication cost is distributed more evenly between nodes.
This is especially true with a lazy push approach where the node who just received a message would push the message ID (e.g. digest) to its $f$ random neighbours,
and only push the full message if the neighbour explicitly requests the message~\cite{leitao2007epidemic}.
With this, nodes typically only need to receive one consensus result message instead of $n$.
